A Continuous Occlusion Model for Road Scene Understanding

### 2016-04-14 CVPR/Source/figure_introduction.tex
Created presentation and poster for mid west vision conference.

\section{Introduction}

%Occlusions present a significant challenge to scene understanding.

As a two-dimensional (2D) projection of the three-dimensional (3D) world, image formation is associated with a loss of information. This is especially significant when objects in 3D space occlude each other with respect to the camera viewpoint. In recent years, we have seen remarkable progress in various aspects of scene understanding, such as structure from motion (SFM) and object detection. However, occlusions still present a challenge, with the difficulty of physically modeling them being a major bottleneck. 
%Prior works have considered occlusions in 2D or through discrete occluder patterns

\begin{figure}[!!t]
\begin{center}
\includegraphics[width=\linewidth]{graphics/figure1.png}
\end{center}
\vspace{-0.6cm}
\caption{\small We propose an occlusion model in 3D that is physically-inspired and continuous. Given object detection and SFM point tracks, our unified model probabilistically assigns point tracks to objects and reasons about object detection scores and bounding boxes. It uniformly handles static and dynamic objects, thus, outperforms motion segmentation for association problems. We also demonstrate occlusion-aware 3D localization in road scenes.}
\label{fig:page1}
\vspace{-0.4cm}
\end{figure}

Our main contribution is a novel theoretical model for occlusion handling that is continuous and fully 3D. Our model is motivated by insights from computer graphics, whereby we represent objects as translucent 3D ellipsoids. In Section \ref{sec:setup}, we develop novel continuous models for representing \emph{transmission} and \emph{reflection} probabilities for each ray emanating from the camera. This allows assigning probabilities for each point in space belonging to an object, which can explicitly explain image observations and reason about occlusions. This is in contrast to prior works that consider occlusions in 2D, or through discrete occluder patterns or models that are not physically interpretable \cite{Pepik_etal_2012,Pepik_etal_2013,Xiang_Savarese_2013,Zia_etal_2013,Zia_etal_2014,Zia2015}.

A key advantage afforded by our occlusion model is unification. While previous approaches to handling occlusions are application-dependent, ours is physically-inspired, thus, flexible enough to be used in a variety of scenarios. In this paper, we show that our theory can be used for uniformly modeling the association of SFM point tracks with static or dynamic objects (Section \ref{sec:association}), as well as modeling object detection scores in applications like 3D localization (Section \ref{sec:localization}). We demonstrate the application of our formulations for road scenes from the KITTI raw dataset \cite{Geiger_etal_2012}.

In particular, assigning 2D point tracks to independent, but potentially occluding, objects is a fundamental challenge in computer vision problems such as multibody SFM \cite{Ozden_etal_2010}. Recent works use motion segmentation \cite{Brox_Malik_2010,Rao_etal_2010} as a precursor to localizing objects, which often suffices for moving objects \cite{Tron_Vidal_2007} and has also been considered for multibody SFM \cite{Kundu_etal_2011}. However, motion-based segmentation is not always applicable in road scenes, due to static parked cars, or dynamic cars that move with similar velocities. Occlusions make the problem more severe since point tracks get clustered together for static objects and may frequently appear to change association among dynamic objects in 2D.
%In contrast, we leverage the success of 
Indeed, we show in Section \ref{sec:experiments} that our point track association outperforms state-of-the-art motion segmentation methods, as well as a baseline that uses detection bounding boxes but does not consider occlusions.

Another potential application of our proposed model is towards 3D localization in road scenes. Prior works such as \cite{Song_Chandraker_2015} combine information from point tracks and detection bounding boxes, but do not consider occlusions for either. In contrast, our unified occlusion model allows a probabilistic soft assignment of point tracks to objects, as well as an occlusion-aware interpretation of object detection outputs. Our model is continuous, so it remains amenable to the use of continuous optimization tools.

To summarize, our main contributions are:
\vspace{-0.2cm}
\begin{tight_itemize}
%\setlength\itemsep{0cm}
\item A novel theoretical model for handling occlusions that is continuous and formulated in 3D.
\item Unified occlusion handling for point tracks in SFM and bounding boxes and detection scores in object detection.
\item Application of our model to association of point tracks with both static and moving objects, improving over motion segmentation and occlusion-unaware baselines.
\item Application of our unified formulation to 3D localization of traffic participants in road scenes.
\end{tight_itemize}

%A fundamental problem in computer vision is to separate feature points of multiple objects which are tracked through a video sequence. The assignments of point tracks to objects can serve as an important preprocessing step for different applications such as 3D localization and reconstruction, where the point tracks associated with an individual object can be used to localize or reconstruct the object in 3D space accurately. In this paper, we focus on road scenes in autonomous driving applications which often include dynamic and static objects simultaneously. For example, some cars are parked near the curb while other cars are moving on the street.

%Motion segmentation approaches~\cite{Rao_etal_2010,Brox_Malik_2010} usually rely on object motions for clustering point tracks. Since point tracks of the same object possess similar motion patterns, these methods generally produce accurate point-to-object associations for dynamic objects~\cite{Tron_Vidal_2007}. However, when there are static objects in the scene, their corresponding point tracks are often clustered together, which decreases the performances significantly and makes motion segmentation approaches unsuitable for road scenes with combinations of dynamic and static objects. Moreover, object occlusions are frequently involved in road scenes, where cars are relatively close to each other and move in the same directions, which makes the problem of point-to-object association for road scene understanding become more challenging.

%In this work, we first propose to model objects as 3D ellipsoids. Motivated by image formulation theory in computer graphics, we then develop novel continuous models for representing \emph{transmission} and \emph{reflection} probabilities, which can explicitly explain image observations and reason about object occlusions. Leveraging on the success of object detection and tracking algorithms~\cite{Felzenszwalb_etal_2010,Choi_Savarese_2010}, we assume that detection bounding boxes and object tracklets are provided, thus we concentrate on segmenting point tracks that are computed only within object tracklets~\cite{Zach2007}, including both dynamic and static point tracks. As we will show in the experiments, the proposed continuous occlusion modelling method outperforms the baseline method which merely uses bounding boxes for dealing with occlusions. Furthermore, our method is not based on object motions and hence does not suffer from static objects as other state-of-the-art motion segmentation methods~\cite{Rao_etal_2010,Brox_Malik_2010}.

%As another important contribution, we examine the applicability of the proposed model for 3D localization in autonomous driving. In contrast to the bounding box baseline method, which uses hard assignments of point tracks to objects (i.e., $\{0,1\}$ probabilities), our continuous occlusion modelling method employs soft assignments (i.e., [$0,1$] probabilities). Consequently, it offers a \emph{unified} continuous occlusion modelling for both point track and bounding box energies, which allows the use of effective continuous optimization tools. As we will show later, the proposed model benefits the task of 3D localization in autonomous driving in terms of lower translation and dimension errors compared to those of~\cite{Song_Chandraker_2014}, which employs bounding boxes for point-to-object associations.

%The rest of the paper is organized as follows: Section~\ref{sec:related} discusses related work. Section~\ref{sec:setup} describes the proposed continuous occlusion model for road scene understanding. Section~\ref{sec:experiments} presents detailed experiments for point-to-object association and 3D localization. Finally, we conclude in Section~\ref{sec:conclusions}.

%The problem of segmenting points to objects often comes up in different computer vision problems especially in multi-body reconstruction and localization. Given correspondence points on consecutive frames, the problem becomes one of finding out which points belong to which object, following which one can use the consensus of segmented points to reconstruct or localize the object more accurately. Without additional information, this is a very difficult problem as attempted by semantic segmentation and motion segmentation methods. However, in the problems like reconstruction and localization one can use the hypothesis of the algorithm as the feedback.
% What is the problem we are trying to solve, and why is it even important?

% What did we do We propose a novel model for representation of objects in the scene so that point tracks can be probabilistically associated with objects while accounting for object occlusions.
% Why is it novel

%Although our proposed model is inspired by Milan et al.\cite{Milan_etal_2014}, it is more detailed and more principled than their work. Milan et al. used soft ellipses and sigmoids to model pedestrians and their occlusions. Our reasoning is instead in 3D. We use ellipsoids to model objects and reason about their occupancies of the space to model their occlusions.
% Ok you proposed a model is it of any use
% How does it compare to state of art
% We show that our continuous occlusion model achieves significantly lower point-to-object association errors compared to the baseline method using detection bounding boxes and other state-of-the-art methods for motion segmentation~\cite{Brox_Malik_2010, Rao_etal_2010}. As a consequence, our model benefits the task of 3D localization of traffic participants in autonomous driving.

>>>>

\begin{center}
  \includegraphics[width=\linewidth]{graphics/figure1.png}
\end{center}
\vspace{-0.6cm}
\caption{\small We propose an occlusion model in 3D that is physically-inspired and continuous. Given object detection and SFM point tracks, our unified model probabilistically assigns point tracks to objects and reasons about object detection scores and bounding boxes. It uniformly handles static and dynamic objects, thus, outperforms motion segmentation for association problems. We also demonstrate occlusion-aware 3D localization in road scenes.}
\label{fig:page1}

### 2016-04-14 poster/poster.tex
Cleaner and working version of repository.
Created presentation and poster for mid west vision conference.

\documentclass[final]{beamer}
\usepackage{beamerposter}
\usepackage{graphicx}			% allows us to import images

\usepackage{bm}
\usepackage{tikz}

@@

@@

\title{3D object localization in road scenes using graphical models}
\author{Vikas Dhiman \and Manmohan Chandrakar \and Jason J Corso}
\institute{University of Michigan}

@@

\begin{frame}[t]
  \begin{columns}[t]												% the [t] option aligns the column's content at the top
  \begin{column}{\sepwid}\end{column}			% empty spacer column
    \begin{column}{\onecolwid}
      \begin{block}{Introduction}
        To accomplish fully or partial autonomous driving we need 3D
        localization of traffic participants in the scene. 
        Since laser scanners and stable wide--baseline stereo setups are
        expensive, we focus on solving the problem using monocular video, GPS
        and maps as our input. Given the video we extract detection bounding
        boxes, ground plane and point tracks.
        We formulate the problem of 3D localization in a probabilistic graphical
        model specifically a factor graph model. We use additional heuristic
        constraints like collision constraint, that leads to a global consistent solution.
        Using these multiple sources of information that provide, possibly conflicting, evidence about
        the location of traffic participant, a consistent meaningful solution must be estimated. 
        We formulate the problem in factor graph
        formalism and use off-the-shelf methods for inference.

        % Related work
        %One of the central goals of 3D scene understanding is to localize the 3D positions and orientations of objects in complex scenes.
        Using
        stereo imagery, several visual cues are combined in \cite{Geiger_etal_2014} to
        simultaneously determine object locations and a rough intersection topology.
        Similar to us, other works have also considered monocular frameworks. Notably,
        occlusions are explicitly handled in \cite{Wojek_etal_2013} by considering
        partial object detectors. A detailed part-based representation of objects based
        on annotated CAD models is used for monocular scene understanding in
        \cite{Zia_etal_2013,Zia_etal_2014}, which also allows reasoning about mutual
        occlusions between objects. In contrast to these works, our monocular framework
        uses a physical modeling of occlusion in continuous space, which makes it more
        general, extensible and amenable for continuous optimization.
      \end{block}

      \begin{block}{Modeling}
        \begin{figure}
          \centering
          \newcommand{\imagewidth}{\onecolwid}
          \input{Source/scenelayoutoverlayCity0961}
          \caption{A sample road scene with the unknowns of each car modeled as random variables. 
          The relating energies are shown in Figure~\ref{fig:graphmodel}}
        \end{figure}

        \begin{figure}
          \centering
          \input{Source/graphical_model_multiple}%
          \caption{Graphical model showing the factor nodes among different
            cars in the same frame. We assume occlusion relationships between
            different cars are known and hence the occlusion modeling can be done
            locally. In this example, the occlusion relationship affects the
            following pair of cars 6-2, 2-5, 5-1. Cars 3 and 4 are not occluded
            and hence affected by only unary terms within the frame. We also avoid 
            collision modeling between unoccluded cars to encourage sparsity.
          }
          \label{fig:graphmodel}
        \end{figure}

      \end{block}
    \end{column}

  \begin{column}{\sepwid}\end{column}			% empty spacer column

    \begin{column}{\onecolwid}
      %\begin{block}{}
        \begin{figure}
          \centering
          \input{Source/graphicalmodelTP}
          \caption{Graphical model showing the factorization of energies for a
            single car. The six state variables of the car can be divided into
            pose $\pos{i}{t}$ and dimensions $\dimsn{i}$. Different energies
          depend only on either of those.}
        \end{figure}
      %\end{block}

      \begin{block}{Energies}
        \begin{table}[h]
          \begin{tabular}{|l|l|}
            \hline
            Symbol & Meaning \\
            \hline
            $\pos{i}{t}$ & Position of $i$th car at time $t$\\
            $\ori{i}{t}$ & Orientation of $i$th car at time $t$\\
            $\dimsn{i}$ & 3D bounding box of the car (dimensions)\\
            $\state{i}{t}$ & State of car $=\{\pos{i}{t}, \ori{i}{t}, \dimsn{i}\}$\\
            $\egop$ & Position of camera at time $t$\\
            $\egoo$ & Orientation of camera at time $t$\\
            $\relp{i}{t}$ & Relative car pose w.r.t. camera \\
            $\tracklets$ & 3D points tracked on car $i$ in its own frame\\
            $\trackp{t}$ & Projection of $\tracklets$ in camera\\
            $\projectionOf{.}$ & Projection function for pose $\relp{i}{t}$\\
            $\bb{i}$ & 2D bounding box of the car in image\\
            \hline
          \end{tabular}
        \end{table}

        Assume conditional independence according to graphical model in
        Figure~\ref{fig:graphmodel}, the negative log likelihood of required
        random variables is given by
        \begin{multline}
          -\log{P(\{\state{i}{t}\} | \mathbb{E})} = 
          Z' + 
          \left(
            \sum_{i=1}^N \sum_{t=s_i}^{e_i}
            \WEnergy{lane} \right.\\
            \left.
            + \WEnergy{size}
            + \WEnergy{dyn}
            + \WEnergy{prior}
            \vphantom{ \sum_{i=1}^N \sum_{t=s_i}^{e_i} }
          \right)\\
          +
          \left(
            \sum_{i,j:i\ne j}^N \sum_{t=s_i}^{e_i}  \WEnergyCol
            + \WpEnergy{box}
            + \WpEnergy{track}
          \right)
          \enspace.
        \end{multline}
      \end{block}
      \begin{block}{Point tracks with occlusion}
        We model continuous point tracks energy with explicit occlusion reasoning as
        the expected re-projection error over the association probability,

        \begin{align}
          \pEnergy{track}(.) =
          %\sum_{t = s_i}^{e_i}
          \sum_{j = 1}^{M}
          \int_1^\infty \assocP\Ereproj(\lambda) d\lambda
        \end{align}
        where $\assocP$ is the association probability of
        $j$\textsuperscript{th} point with $i$\textsuperscript{th} TP at depth $\lambda$
        and $\Ereproj(\lambda)$ is the re-projection error given by
        %
        \begin{align}
          \assocP &= \Prefl\Ptrans\\
          \Ereproj(\lambda) &= \left\|\trackpj{t+1} - \projectionOft{\invProjectionOf{\trackpj{t}, \lambda}}\right\|^2 .
          \label{eq:reprojerror}
        \end{align}

      \end{block}

    \end{column}

  \begin{column}{\sepwid}\end{column}			% empty spacer column

    \begin{column}{\onecolwid}

      \begin{block}{Object detection with occlusion}
        To account for occlusion we weight the error along each side of the
        bounding box with a visibility fraction that is proportional to
        unoccluded area around that side:
        \begin{align}
          \pEnergy{occ}(.) =
          \bm{\rho}^{ij}(t)^\top\left|\projectionOf{\dimsn{i}} - \bb{i}\right|
          \enspace,
          %\sum_{i=1}^N \sum_{t=s_i}^{e_i}
          %\sum_kp_{ik}^{\text{track}}(\projectionOf{\dimsn{i}} - \bb{k})^\top \pmb{\rho}(i,j,t)
        \end{align}
        where $\bm{\rho}^{ij}(t)$ is the visibility fraction vector of the side
        of the bounding box.

      \end{block}

      %\begin{block}{Object detection with continuous occlusion}
      %  The detection scores GMM with occlusion is given by replacing the covariance
      %  matrix
      %  %
      %  \begin{multline}
      %    S'(\bb{i}) =\\
      %    \sum_j A_j \exp(-(\bb{i}-\mu^{(d)}_j)^\top \Sigma'^{(d)-1}_j
      %    (\bb{i}-\mu^{(d)}_j))
      %  \end{multline}

      %  The energy of detection scores is simply take to be the inverse of the detection score.
      %  \begin{align}
      %    \Energy{detect}(\{ \relp{i}{t} \}_i, \{ \relp{i}{t-1} \}_i, \{\dimsn{i}\}_i ) = \frac{1}{S'(\bb{i})}
      %  \end{align}
      %\end{block}

      \begin{block}{Other Energies}
        \begin{description}
          \item[Lane energy]
            \begin{multline}
              \label{eq:laneOrientationEnergy}
              \Energy{lane} = 
              \sum_{m \in M_{\text{close}}}
              (1 - \ori{i}{t} \cdot \text{tan}(L_{m}(k), \pos{i}{t}) )
              \LaneUncertainty{\pos{i}{t}}
            \end{multline}
            where $M_{\text{close}} = \{m : \text{dist}(L_{m}(k), \pos{i}{t}) < 50\} $ is
            the set of nearby lanes and 
            \begin{multline}
              \LaneUncertainty{\pos{i}{t}} = 
              \frac{1}{1 + \exp{(-q(w_{\text{road}} - \text{dist}(L_{m}(k), \pos{i}{t})))}}
            \end{multline}
            for some constant $w_{\text{road}}$ that represents the width of the road.

          \item[Holonomic energy]
            \begin{align}
              \label{eq:totalPosTransitionEnergy}
              \Energy{dyn} = 1 - \ori{i}{t-1} \cdot (\pos{i}{t} - \pos{i}{t-1})
            \end{align}

            %\begin{align}
            %  \Energy{dyn-ori} &= \|\ori{i}{t} - \ori{i}{t-1}\|^2\\
            %  \Energy{dyn-vel} &= \|(\pos{i}{t} - 2\pos{i}{t-1}) + \pos{i}{t-2}\|^2
            %\end{align}

            %\begin{align}
            %  \WEnergy{dyn} &= \WEnergy{dyn-hol} + \WEnergy{dyn-ori} + \WEnergy{dyn-vel}
            %\end{align}

          %\item[Collision Energy]
          %  \begin{align}
          %    \label{eq:collisionEnergyHellingerDistance}
          %    \EnergyCol = -\log\left(
          %      A_{ij}
          %      e^{-\frac{1}{8}
          %        \left(\pos{i}{t} - \pos{j}{t}\right)^\top
          %        P^{-1}
          %        \left(\pos{i}{t} - \pos{j}{t}\right)
          %      }
          %    \right)
          %  \end{align}

          \item[Size Prior]
            \begin{align}
              \label{eq:totalSizeEnergy}
              \Energy{size} &= (\dimsn{i} - \expDimsn)^\top\Sigma_{\expDimsn}^{-1}(\dimsn{i} -
              \expDimsn)
            \end{align}

            where $\expDimsn$ is the mean TP dimensions and
            $\Sigma_{\expDimsn}$ is the correspondence covariance matrix.

        \end{description}
      \end{block}
      \begin{block}{Experiments and Results}
        We perform experiments on KITTI \cite{geiger2013vision} dataset.
        \includegraphics[width=\onecolwid]{results/Visualization/City/2011_09_26_drive_0009/single_window_contPtTracks_size_bboxOcc_yawTstepWiseInference/0000000061.png}\\
        \includegraphics[width=\onecolwid]{results/Visualization/City/2011_09_26_drive_0009/single_window_lane_size_bboxOcc_yawTstepWiseInference/0000000061.png}\\

      \end{block}
    \end{column}

  \begin{column}{\sepwid}\end{column}			% empty spacer column

    \begin{column}{\onecolwid}
      \begin{block}{}
        \includegraphics[width=\onecolwid]{results/Visualization/City/2011_09_26_drive_0009/single_window_contPtTracks_size_bboxOcc_yawTstepWiseInference/0000000063.png}
      \end{block}
      \begin{table}
        \begin{tabular}{|l|l|r|r|r|}
          \hline
          Energy & Metric & Occ & Unocc & Total\\
          \hline
contPtTracks+size+bboxOcc+yawT  &t  &2.636&4.499&3.351\\
                                &yaw&0.130&0.201&0.159\\
                                &dim&0.971&1.042&1.005\\
          \hline
contPtTracksNoOcc+size+bbox+yawT&t  &2.648&4.488&3.355\\
                                &yaw&0.126&0.197&0.156\\
                                &dim&0.964&1.051&1.006\\
          \hline
                  size+bbox+yawT&t  &2.616&4.501&3.349\\
                                &yaw&0.125&0.231&0.166\\
                                &dim&0.969&1.024&0.997\\
          \hline
               size+bboxOcc+yawT&t  &2.615&4.505&3.350\\
                                &yaw&0.125&0.231&0.166\\
                                &dim&0.969&1.008&0.991\\
          \hline
          (Init only)           &t  &2.583&4.486&3.321\\
                                &yaw&0.113&0.181&0.143\\
                                &dim&0.768&0.864&0.819\\
          \hline

        \end{tabular}
      \end{table}
      \begin{block}{Conclusion}
        We use Probablistic graphical models to deduce consistent solutions from multiple sources. The results do not match our expectations and hence need further investigation.
      \end{block}
      \begin{block}{References}
        {\small
          \bibliographystyle{ieee}
          \bibliography{continuousocclusion}
        }
      \end{block}
    \end{column}

  \begin{column}{\sepwid}\end{column}			% empty spacer column

  \end{columns}
\end{frame}
\end{document}

\setbeamercolor{block alerted title}{fg=black,bg=norange}	% frame color
\setbeamercolor{block alerted body}{fg=black,bg=white}		% body color
\begin{alertblock}{Alert Block Colours}
  You can similarly modify the colours for alert blocks (but try not to overdo it):\\
  \begin{semiverbatim}
  {\color{red}\\setbeamercolor}\{block title\}\newline \{fg=black,bg=norange\}
  \end{semiverbatim}
  \begin{semiverbatim}
  {\color{red}\\setbeamercolor}\{block  body\}\newline \{fg=black,bg=white\}
  \end{semiverbatim}
\end{alertblock}

>>>>

\documentclass[handout,final]{beamer}
\usepackage{beamerposter}
\usepackage{graphicx}			% allows us to import images

\usepackage{booktabs}
\usepackage{bm}
\usepackage{tikz}

@@

\newcommand{\Ptransmission}{P_{\textit{transmission}}}%

@@

\title{A Continuous Occlusion Model for Road Scene Understanding}
\author{Vikas Dhiman$^\dagger$ \and Quoc-Huy Tran$^*$ \and Jason J Corso$^\dagger$ \and Manmohan Chandraker$^*$}
\institute{$^\dagger$University of Michigan, Ann Arbor, MI \qquad $^*$NEC Labs, Cupertino, CA}

@@

\begin{frame}[t]
  \begin{columns}[t]												% the [t] option aligns the column's content at the top
    \begin{column}{\sepwid}\end{column}			% empty spacer column
    \begin{column}{\onecolwid}
      \begin{block}{Introduction}
        \begin{figure}[!!t]
          \input{Source/figure_introduction.tex}
        \end{figure}
      \end{block}

      \begin{block}{Continuous Occlusion Model}
        \begin{align}
          f^i_{\text{occ}}(\bx) = \cL(\bx; \bp_i, \bSigma_i),
        \end{align}
        \begin{align}
          P^{ij}_{\textit{observation}} = P^{ij}_{\textit{reflection}}P^{j}_{\textit{transmission}}.
          \label{eq:imgform}
        \end{align}
        \begin{align}
          \Prefl = \frac{1}{Z}(\max \{0, \nabla {f^i_{occ}}(\bx_j)^\top \ray \})^2.
          \label{eq:evalPrefl}
        \end{align}

        \begin{align}
          P^j_{\textit{transmission}}(\lambda) &= \prod_{c}^{\lambda} (1 - \occft{\lambda \ray})^{d\lambda}\\
          &\approx \prod_i (1 - \cL_u (\bu; \bmu_i, \bGamma_i) \cL_{\lambda}(\lambda; \meandepth{i})).
          \label{eq:ptrans-integral}
        \end{align}

        % \begin{figure}
        %   \usetikzlibrary{calc}
        %   \centering
        %   \begin{tikzpicture}
        %     \input{Source/reflectiontransmissiongraph.tex}
        %   \end{tikzpicture}
        %   \vspace{-0.3cm}
        %   \caption{\small We represent objects as translucent ellipsoids, which leads to the formulation of transmission and reflection probabilities. This figure shows the reflection probability for the first object (in violet), which has high values around the camera-facing side of the object. Also, note that the transmission probability is inversely proportional to occupancy.}
        %   \label{fig:reflectiontransimission}
        %   \vspace{-0.3cm}
        % \end{figure}
        \begin{figure}
          \centering
          \includegraphics[width=0.9\columnwidth]{results/plotPtransmission_exact_vs_approx_pt_vis-small.png}\\
          \includegraphics[trim=0.0 0 0.3in 0, clip, width=0.9\columnwidth]{results/plotPtransmission_exact_vs_approx_embedded_fonts.pdf}
          \vspace{-0.3cm}
          \caption{\small Comparisons between the approximate and exact formulations of $\Ptrans$. The drop in the approximate version is delayed because we assume drop at the object center rather than the camera-facing face of the object.}
          \label{fig:compare:exact:approx:ptrans}
          \vspace{-0.3cm}
        \end{figure}
      \end{block}

    \end{column}
    \begin{column}{\sepwid}\end{column}			% empty spacer column
    \begin{column}{2.0\onecolwid}
      \begin{block}{Results}
        \vspace*{-\baselineskip}
        \begin{columns}[t]
          \column{1.000\onecolwid}
          \begin{table}
            \begin{tabular}{lrrrr}
              \toprule
              Point tracks & Ours & BBox & BM & RAS\\
              \midrule
              Dynamic \& occluded         & \textbf{13.2} & 21.3 & 30.9 & 30.1 \\
              Occluded		              & \textbf{15.7} & 19.8 & 39.5 & 37.8 \\
              Dynamic		              & \textbf{6.6} & 11.4 & 15.3 & 17.7 \\
              All		                  & \textbf{8.6} & 12.6 & 21.9 & 21.5 \\
              \bottomrule
            \end{tabular}
            \caption{\small Mean association errors on different sets of input point tracks over all sequences. Errors are in terms of average fractions of foreground points incorrectly associated to objects per sequence.}
            \label{tab:meanAssoc}
          \end{table}
          \column{1.000\onecolwid}
          \begin{table}
            \begin{tabular}{lrr}
              \toprule
              Method & t & dim \\
              \midrule
              Point cloud fitting
              & 6.87 & 4.02\\
              Initialization by~\cite{Song_Chandraker_2014}
              & 5.61 & 3.23\\
              $\EnergyTrackNoOcc + \EnergyBBoxNoOcc +\EnergySize+\EnergyDyn$ 
              & 3.95  & 1.72\\        
              $\EnergyTrackNoOcc + \EnergyBBox +\EnergySize+\EnergyDyn$        
              & 4.81  & 2.16\\        
              $\EnergyTrack + \EnergyBBoxNoOcc +\EnergySize+\EnergyDyn$      
              & 4.05  & {\bf 1.59}\\        
              $\EnergyTrack + \EnergyBBox +\EnergySize+\EnergyDyn$             
              & {\bf 3.24}  & 2.16\\
              \bottomrule
            \end{tabular}
            \caption{\small Localization experiment results with different combinations of energies. We report translation error (t) and dimension error (dim) in meters per car. Yaw angles for static objects are not optimized by our model. These experiments use the set of occluded tracks to demonstrate the effect of our modeling.}
            \label{tab:localizationExperiment}
          \end{table}
        \end{columns}
      \end{block}

      \begin{block}{Association error}
        \begin{figure}[!!t]
          \centering
          \includegraphics[trim=1.0in 0.4in 1.0in 0.2in, clip, width=0.9\textwidth]{results/plotErrorBarEvalAssocCoeffAllSequence.pdf}
          \vspace{-0.3cm}
          \caption{\small Association errors on different sets of input point tracks. Numbers on the x-axis represent sequence numbers in the KITTI raw dataset. Errors are in terms of average fractions of foreground points incorrectly associated to objects per sequence.}
          \vspace{-0.3cm}
          \label{fig:assoc-occ-results}
        \end{figure}
        \newlength{\tblimgwidth}
        \setlength{\tblimgwidth}{0.080\textwidth}
        \input{Source/figure_assoc_qualitative.tex}
      \end{block}
    \end{column}
    \begin{column}{\sepwid}\end{column}			% empty spacer column
    \begin{column}{\onecolwid}
      \begin{block}{Object Point Association}
        \begin{align}
          \assocP = \Prefl\Ptrans,
          \label{eq:defineassocP}
        \end{align}
        \begin{align}
          P^{ij}_{\text{assoc}} = \frac{1}{Z''}\int_0^{\infty} \assocP \exp(-\Ereproj(\lambda))d\lambda,
          \label{eq:prob-assoc}
        \end{align}
      \end{block}
      \vspace{0.5in}
      \begin{block}{3D Object Localization}
        \begin{figure}
          \centering
          \input{Source/graphical_model_multiple}%
          \caption{Graphical model showing the factor nodes among different
            cars in the same frame. We assume occlusion relationships between
            different cars are known and hence the occlusion modeling can be done
            locally. In this example, the occlusion relationship affects the
            following pair of cars 6-2, 2-5, 5-1. Cars 3 and 4 are not occluded
            and hence affected by only unary terms within the frame. We also avoid 
            collision modeling between unoccluded cars to encourage sparsity.
          }
          \label{fig:graphmodel}
        \end{figure}
        \begin{multline*}
          -\log{P(\{ \bp^i(t) , \bomega^i(t) , \bB^i(t) \} | \{\bu_j(t)\} , \{\bb{i}\} )} = \\
          -\tilde{Z} 
          + \sum_{t=s_i}^{e_i} \lambda_{\text{track}}\EnergyTrack
          + \\ 
          \sum_{t=s_i}^{e_i} \sum_{i=1}^N  
          \left(
            \lambda_{\text{detect}}\EnergyBBox
            + \lambda_{\text{dyn}}\EnergyDyn    
            + \lambda_{\text{size}}\EnergySize
          \right)
          \enspace,
        \end{multline*}
        \begin{equation}
          \Ereproj(\lambda) = \left\|\trackpj{t} - \projectionOf{\invProjectionOftm{\trackpj{t-1}, \lambda}}\right\|^2.
          \label{eq:reprojerror}
        \end{equation}
        % \begin{figure}
        %   \centering
        %   \newcommand{\imagewidth}{\onecolwid}
        %   \input{Source/scenelayoutoverlayCity0961}
        %   \caption{A sample road scene with the unknowns of each car modeled as random variables. 
        %   The relating energies are shown in Figure~\ref{fig:graphmodel}}
        % \end{figure}

      \end{block}
      \vspace{0.5in}
      \begin{block}{Conclusions and Future work}
        \begin{itemize}
          \item Presented physically interpretable unified occlusion modeling
          \item The model generalizes to different applications: point association and 3D localization
          \item Challenges include the slow inference on 3D localization
        \end{itemize}
      \end{block}
      \vspace{0.5in}
      \begin{block}{Acknowledgements}
        This work was part of V.~Dhiman's internship at NEC Labs America, in Cupertino. V.~Dhiman and J.~J.~Corso were also supported by NSF NRI IIS 1522904.
      \end{block}
      \begin{block}{References}
        \bibliography{poster}
        \bibliographystyle{ieee}
      \end{block}
    \end{column}
  \end{columns}
\end{frame}

\end{document}
